---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dhmisc

[![CRAN status](https://www.r-pkg.org/badges/version/dhmisc)](https://CRAN.R-project.org/package=dhmisc)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

**dhmisc** is a collection of functions/tools I like to use but are either not present in any R packages I know of or their implementation in existing R packages don't fulfill my needs.

## Installation

Development version:

```{r, eval=FALSE}
remotes::install_github("dhersz/dhmisc")
```

## Functions

The package doesn't yet contain any functions.

The pre-commit hooks were basically copied from the great [`precommit`](https://github.com/lorenzwalthert/precommit) package. The hooks I want to use don't work in my computer due to `bash` location, so I had to adapt the shebang a small bit.

To install and use `precommit` please check its [installation and usage instructions](https://github.com/lorenzwalthert/precommit#installation). After running `precommit::use_precommit()` you will need to adjust the `.pre-commit-config.yaml` to use the hooks provided here. An example on how to do it will soon be provided.

## Acknowledgement

Credits for pre-commit hooks go to [Lorenz Walthert](https://github.com/lorenzwalthert), [`precommit`](https://github.com/lorenzwalthert/precommit) maintainer.
